---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# frbinom

<!-- badges: start -->
<!-- badges: end -->

The goal of frbinom is to generate random variables of fractional binomial distribution and compute its density, cumulative distribution, and quantiles. 

## Installation

You can install the development version of frbinom from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("leejeo25/frbinom")
```

## Example

10 random variables of a fractional binomial distribution.

```{r}
library(frbinom)
rfrbinom(n=10, size=50, prob=.6, h=.8, c=.2)
```

The probability density of the fractional binomial distribution.

```{r}
dfrbinom(x=seq(0,50,1), size=50, prob=.6, h=.8, c=.2)
```

The histogram of the fractional binomial random variables overlaid with its density.
```{r}
simu.<-rfrbinom(10000, 50, .6, .7, .2)
den.<-dfrbinom(seq(0,50,1), 50, .6, .7, .2)
hist(simu., breaks=51, probability = TRUE)
lines(seq(0,50,1), den., type="l")
```


